Improved association in a classical density functional theory for water

### 2014-01-16 papers/water-saft/paper.tex
Small changes to water paper. Tested on knightley. Took 0:39.65.

\begin{abstract}
We present a modification to our recently published SAFT-based classical
density functional theory for water.
%
We have recently developed and tested a functional for the averaged
radial distribution function at contact of the hard-sphere fluid
that is dramatically more accurate at interfaces than earlier
approximations.
%
We now incorporate this improved functional into the association term
of our free energy functional for water, improving its description of
hydrogen bonding.
%
We examine the effect of this improvement by studying two hard solutes: a
hard hydrophobic rod and a hard sphere.
%
The improved functional leads to a moderate change in the density
profile and a large decrease in the number of hydrogen bonds broken in
the vicinity of the solutes.  \fixme{It improves agreement with experiment...}
\end{abstract}
\maketitle

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/Kr-278K-densities}
\end{center}
\caption{ $g$ for Kr and water at low temperature high pressure...}
\label{fig:g-Kr}
\end{figure}

>>>>

\begin{abstract}
We present a modification to our recently published SAFT-based classical
density functional theory for water.
%
We have recently developed and tested a functional for the averaged
radial distribution function at contact of the hard-sphere fluid
that is dramatically more accurate at interfaces than earlier
approximations.
%
We now incorporate this improved functional into the association term
of our free energy functional for water, improving its description of
hydrogen bonding.
%
We examine the effect of this improvement by studying two hard solutes(a
hard hydrophobic rod and a hard sphere) \fixme{and a Lennard-Jones solute.}
%
The improved functional leads to a moderate change in the density
profile and a large decrease in the number of hydrogen bonds broken in
the vicinity of the hard solutes.  
%
We find an improvement of the radial distribution for a Lennard-Jones
Krypton atom in water.
\end{abstract}
\maketitle

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figs/Kr-278K-densities}
\end{center}
\caption{ $g$ for Kr and water at low temperature ($5^\circ$ C) and high
  pressure (110 bar).}
\label{fig:g-Kr}
\end{figure}
